---
title: "Atanga Longhi models"
author: "Christina Boxberger"
date: "3/31/2022"
output: html_document
---

## Load packages and data
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(GGally)
library(MuMIn)
```

```{r load-data}
setwd("~/bass")
Atanga_Longhi <- read.csv("Atanga_Longhi.csv", header = T, na.string = "")
```

## Clean Data

```{r no-nas}
sapply(Atanga_Longhi, class)

Atanga_Longhi$Ethnicity[Atanga_Longhi$village %in% c("Indombo", 
                                             "Mayela I", 
                                             "Bombenda", 
                                             "Massaha", 
                                             "Etakaniabe")] <- "Kota"

Atanga_Longhi$Ethnicity[Atanga_Longhi$village %in% c("Nsiete", 
                                             "Ntenkele")] <- "Fang"

Atanga_Longhi <- na.omit(Atanga_Longhi)
```
 
## Atanga Models

```{r atanga1}
atanga1 <- glm(Atanga ~ Distance + 
                 factor(Ethnicity) + 
                 factor(Gender) + 
                 factor(Age) + 
                 factor(Farmer) + 
                 factor(Hunter), 
               family = binomial, 
               data = Atanga_Longhi)

summary(atanga1)
```

(omit gender)

```{r atanga2}
atanga2 <- glm(Atanga ~ Distance + 
                 factor(Ethnicity) + 
                 factor(Age) + 
                 factor(Farmer) + 
                 factor(Hunter), 
               family = binomial, 
               data = Atanga_Longhi)

summary(atanga2)
```

(omit age)

```{r atanga3}
atanga3 <- glm(Atanga ~ Distance + 
                 factor(Ethnicity) + 
                 factor(Farmer) + 
                 factor(Hunter), 
               family = binomial, 
               data = Atanga_Longhi)

summary(atanga3)
```

(omit ethnicity)

```{r atanga4}
atanga4 <- glm(Atanga ~ Distance + 
                 factor(Farmer) + 
                 factor(Hunter), 
               family = binomial, 
               data = Atanga_Longhi)

summary(atanga4)
```
Everything except for "Hunter" got LESS significant here; taking out farmer. 

```{r atanga5}
atanga5 <- glm(Atanga ~ Distance + 
                 factor(Hunter), 
               family = binomial, 
               data = Atanga_Longhi)

summary(atanga5)
```
(omit distance)

```{r atanga6}
atanga6 <- glm(Atanga ~ factor(Hunter), 
               family = binomial, 
               data = Atanga_Longhi)

summary(atanga6)
```
Hunter and intercept both significant!

```{r atanga-aic}
AIC(atanga1, atanga2, atanga3, atanga4, atanga5, atanga6)

AICc(atanga1, atanga2, atanga3, atanga4, atanga5, atanga6)
```

### atanga5 (Hunter, Distance) has the lowest AIC!

## Longhi Models

```{r longhi1}
longhi1 <- glm(Longhi ~ Distance + 
                 factor(Ethnicity) + 
                 factor(Gender) + 
                 factor(Age) + 
                 factor(Farmer) + 
                 factor(Hunter), 
               family = binomial, 
               data = Atanga_Longhi)

summary(longhi1)
```

(omit gender)

```{r longhi2}
longhi2 <- glm(Longhi ~ Distance + 
                 factor(Ethnicity) + 
                 factor(Age) + 
                 factor(Farmer) + 
                 factor(Hunter), 
               family = binomial, 
               data = Atanga_Longhi)

summary(longhi2)
```

(omit hunter)

```{r longhi3}
longhi3 <- glm(Longhi ~ Distance + 
                 factor(Ethnicity) + 
                 factor(Age) + 
                 factor(Farmer), 
               family = binomial, 
               data = Atanga_Longhi)

summary(longhi3)
```

(omit distance)

```{r longhi4}
longhi4 <- glm(Longhi ~ factor(Ethnicity) + 
                 factor(Age) + 
                 factor(Farmer), 
               family = binomial, 
               data = Atanga_Longhi)

summary(longhi4)
```

(omit farmer)

```{r longhi5}
longhi5 <- glm(Longhi ~ factor(Ethnicity) + 
                 factor(Age), 
               family = binomial, 
               data = Atanga_Longhi)

summary(longhi5)
```
One level of age is significant, and one isn't.

```{r longhi6}
longhi6 <- glm(Longhi ~ factor(Ethnicity), 
               family = binomial, 
               data = Atanga_Longhi)

summary(longhi6)
```
Nothing significant anymore!

```{r longhi-aic}
AIC(longhi1, longhi2, longhi3, longhi4, longhi5, longhi6)
AICc(longhi1, longhi2, longhi3, longhi4, longhi5, longhi6)
```
### longhi5 (Ethnicity, Age) is the best model!